Efficient pedigree recording for fast population genetics simulation

### 2017-12-30 forwards_paper.tex
Suggested tweaks to c++ methods section
& formatting of C++

To demonstrate the method's flexibility and to test it in different contexts,
we implemented these simulations separately using two different simulation engines:

\jda{Note/TODO: the varying references to c++, python, fwdpp, fwdpy11 and
	simupop are probably confusing to a new reader. This is in part because
	we refer to the python/simupop method in various places as one or the
	other; the same goes for c++/fwdpy11/fwdpp. We should decide what to
	call these and make our usage consistent}

\begin{enumerate}

    \item
        In \cpp{}, using \fwdpp{} library functions and interface code (details below),
        using a continuum-sites model for both mutation and recombination. Simulations were run using \fwdpy{}, a Python
        package based on \fwdpp.
        % $\mu$ and $r$ were the means of Poisson processes, and mutations used the infinite-sites model \citep{Kimura1969-uc}.
        % We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$.

@@

%% simplify run time
Above we have described memory requirements;
how does the computation time required for simplification scale?
Simply because it must process each edge,
% below per discussion
% https://github.com/petrelharp/ftprime_ms/pull/37#discussion_r156617283
the simplification algorithm is at least linear in the number of edges of the input tree sequence.
Empirically the algorithm is exactly linear,
as seen in Figure~\ref{fig:simplify_complexity}X,
where we show shows the time required to simplify increasingly large subsets of a large tree sequence.
When simplifying the result of a forwards-time sequence, the number of edges is the main contributing factor.
Suppose on the other hand we want to
simplify an already-minimal but large tree sequence with $N$ nodes
to a subsample of size $n$.
How does the required time scale with $n$?
In this case, the computation is dominated by the size of the output tree sequence,
which grows with $\log(n)$.
this is also seen in Figure~\ref{fig:simplify_complexity}X,
showing the time required to simplify progressively larger subsets of a single large tree sequence.

>>>>

To demonstrate the method's flexibility and to test it in different contexts,
we implemented these simulations separately using two different simulation engines:
\begin{enumerate}

    \item
        In \cpp{}, using \fwdpp{} library functions and interface code (details below),
        using a continuum-sites model for both mutation and recombination. Simulations were run using \fwdpy{}, a Python
        package based on \fwdpp.
        % $\mu$ and $r$ were the means of Poisson processes,
        % and mutations used the infinite-sites model \citep{Kimura1969-uc}.
        % We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$.

@@

%% simplify run time
Above we have described memory requirements;
how does the computation time required for simplification scale?
Simply because it must process each edge,
the simplification algorithm is linear in the number of edges of the input tree sequence.
This is seen in Figure~\ref{fig:simplify_complexity}X,
where we show shows the time required to simplify increasingly large subsets of a large tree sequence.
When simplifying the result of a forwards-time sequence, the number of edges is the main contributing factor.
Suppose on the other hand we want to
simplify an already-minimal but large tree sequence with $N$ nodes
to a subsample of size $n$.
How does the required time scale with $n$?
In this case, the computation is dominated by the size of the output tree sequence,
which grows with $\log(n)$.
this is also seen in Figure~\ref{fig:simplify_complexity}X,
showing the time required to simplify progressively larger subsets of a single large tree sequence.
